Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-10-24 thesis/paper_draft.qmd
add links for reproducible

2. **Recon_Honours_Analysis**: This repository contains all R codes to produce the simulation studies and empirical analysis in this thesis (including scripts to run on a high-performance cluster), along with wrangling, processing, and analysing the results data. It depends on the *ReconCov* package. The access is upon request.

3. **Recon_Honours_Thesis**: This repository contains the thesis manuscript in Quarto format, along with all figures and tables. The access is upon request.

Please contact the author via email `Vincent.Su@monash.edu` for access to the analysis and thesis repositories.

>>>>

2. **Recon_Honours_Analysis**: This repository contains all R codes to produce the simulation studies and empirical analysis in this thesis (including scripts to run on a high-performance cluster), along with wrangling, processing, and analysing the results data. It depends on the *ReconCov* package. It is available at [https://github.com/lordtahdus/Recon_Honours_Analysis](https://github.com/lordtahdus/Recon_Honours_Analysis)

3. **Recon_Honours_Thesis**: This repository contains the thesis manuscript in Quarto format, along with all figures and tables. The access is upon request. [https://github.com/lordtahdus/Recon_Honours_Thesis](https://github.com/lordtahdus/Recon_Honours_Thesis)

Please contact the author via email `Vincent.Su@monash.edu` for specific navigation or questions regarding the code repositories.
